---
title: "SGC Full Regressions"
author: "Matt Alvarez-Nissen"
date: "9/6/2020"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis", message = FALSE, warning = FALSE)
```

```{r read-libraries-parameters, message=FALSE, warning=FALSE}
library(tidyverse)
library(glue)

# Files
## PSM results
total_stats_all_file <- "./SGC/total_stats_all.csv"

## ACS
all_years_tract_ca_file <- "./SGC/tract characteristics/all_years_tract_CA.csv"

## NOAH 
noah_00_file <- "./SGC/NOAH_SGC_2000.csv"
crosswalk_00_10_file <- "./SGC/crosswalk_2000_2010.csv"
```

```{r read-noah-2000, echo= FALSE, warning=FALSE, message=FALSE}
# Read in NOAH data (2000)
noah_00 <- 
  read_csv(noah_00_file) %>% 
  # filter down to necessary columns
  select(
    GEOID = stctytrct,
    noah_housing_tot = housing_tot,
    noah_tot_clean,
    noah_nolihtc_clean,
    d_bay, 
    d_la, 
    d_fresno
  )

# Crosswalk 2000 NOAH to 2010 Census boundaries
## Read in crosswalk file
crosswalk_00_10 <- read_csv(crosswalk_00_10_file)
```

```{r filter-xwalk, warning=FALSE, message=FALSE}
## Filter crosswalk to relevant tract IDs
### Use crosswalk filter from Brown University Diversity and Disparities
### https://s4.ad.brown.edu/projects/diversity/Researcher/LTBDDload/DataList.aspx

# 2000 NOAH
## Create list of FIPS from ACS data to filter on
fips_00_filter <-
  paste(noah_00$GEOID, collapse = "|")

## Filter crosswalk data by relevant FIPS
crosswalk_00_filter <-
  crosswalk_00_10 %>% 
  filter(str_detect(trtid00, fips_00_filter))
```

```{r do-crosswalk, echo=FALSE, warning=FALSE, message=FALSE}
# 2000 NOAH
## Interpolate 2000 boundary data to 2010 tracts
noah_00_xwalk <-
  noah_00 %>% 
  # rename full FIPS code for a join
  rename(trtid00 = GEOID) %>% 
  # join to filtered crosswalk
  full_join(crosswalk_00_filter, by = "trtid00") %>% 
  # change weight from character to numeric type
  mutate(weight = as.numeric(weight)) %>% 
  # multiply all data by its weight
  mutate(
    across(
      # select all NOAH data
      noah_housing_tot:noah_nolihtc_clean,
      # find value of data multiplied by weight
      ~ . * weight, 
      # attach name in the following pattern
      .names = "{col}_00"
    )
  ) %>% 
  # select for relevant variables (2010 tracts)
  select(trtid10, ends_with("_00")) %>% 
  # group by 2010 tracts
  group_by(trtid10) %>% 
  # sum up all variables
  summarise_all(sum) %>% 
  # rename trtid10 to GEOID
  rename(GEOID = trtid10)
```

```{r write-noah-2000-xwalk}
noah_00_xwalk %>% write_csv("./SGC/NOAH_SGC_2000_xwalk.csv")
```

```{r read-psm-results}
total_stats_all <- read_csv(total_stats_all_file)
```

# FIXED EFFECTS NOTES
* Used 2010 for all Granville Properties
* Don't know year for MacArthur Transit Village
* Used Construction Date for Concord
* Don't know year for Crenshaw Boulevard Streetscape Plan (Los Angeles TOD Planning (Round 1))
* Don't know year for Midtown Transportation & Streetscape Improvements
* Don't know year for Rumrill Park
* Don't know year for Salud Park
* Used Construction Date for Ed Roberts Campus
* Used 2015 (2016 flag) for all Taylor Yard Village properties
* Used 2018 flag for Metro Willowbrook/Rosa Parks Station Improvements
* Used 2018 flag for Albion Riverside Park

```{r create-regression-df, warning=FALSE, message=FALSE}
# Prepare data for full regressions
# read in tract data
all_years_tract_ca <- read_csv(all_years_tract_ca_file)

# create regression df
total_reg_df <-
  total_stats_all %>% 
  # create location flags
  mutate(
    la_flag = if_else(location == "LA", 1, 0),
    sf_flag = if_else(location == "SF_Bay", 1, 0)
  ) %>% 
  # remove extra variables
  select(-c(distance, location, n_invest)) %>% 
  # reorder columns
  select(GEOID, investment, la_flag, sf_flag, everything()) %>% 
  # join with census tract data
  left_join(all_years_tract_ca) %>% 
  # join with 2000 NOAH data
  left_join(noah_00_xwalk, by = "GEOID") %>% 
  # rename total NOAH change variables
  rename(
    perc_noah_tot_change_09_16 = perc_noah_tot_change,
    noah_tot_change_09_16 = noah_tot_change
  ) %>% 
  # create percent, percentage point, and unit NOAH change (2000-2009, 2009-2016)
  mutate(
    # unit change (2000-2009)
    noah_tot_change_00_09 = noah_tot_clean_09 - noah_tot_clean_00,
    # % change (2000-2009)
    perc_noah_tot_change_00_09 = 
      noah_tot_change_00_09 / noah_tot_clean_00,
    # % point change (2000-2009)
    perc_pnt_noah_change_00_09 =
      (noah_tot_clean_09 / noah_housing_tot_09) - 
      (noah_tot_clean_00 / noah_housing_tot_00),
    # % point change (2009-2016)
    perc_pnt_noah_change_09_16 =
      (noah_tot_clean_16 / noah_housing_tot_16) - 
      (noah_tot_clean_09 / noah_housing_tot_09)
  ) %>% 
  # Replace all "Inf" values with NA
  mutate(across(.cols = everything(), na_if, Inf)) %>% 
  # match investments to create fixed effects time flags
  pivot_longer(
    cols = c(investment_1:investment_7), 
    values_to = "investment_name"
  ) %>% 
  # clean up investment names
  select(-name) %>% 
  # Group by GEOID
  group_by(GEOID) %>% 
  # create fixed effects dummies - based on Operation Start Date
  # (Construction if not available)
  mutate(
    invest_begin_07 = 
      case_when(
        # SFMTA Third Street Light Rail
        str_detect(investment_name, "Third St") ~ 1,
        TRUE                                    ~ 0
      ),
    invest_begin_10 = 
      case_when(
        ## Concord- Monument Blvd/Meadow Ln Pedestrian Imprvs
        str_detect(investment_name, "Concord")           ~ 1,
        ## Ed Roberts Campus
        str_detect(investment_name, "Ed Roberts")        ~ 1,
        ## Granville Properties, first was completed 2010 - others at later date
        ## lumping all together for now
        str_detect(investment_name, "1612 Fulton St")    ~ 1,
        str_detect(investment_name, "Brio on Broadway")  ~ 1,
        str_detect(investment_name, "Bungalow Court")    ~ 1,
        str_detect(investment_name, "Crichton Place")    ~ 1,
        str_detect(investment_name, "Fulton Village")    ~ 1,
        str_detect(investment_name, "The Lede")          ~ 1,
        str_detect(investment_name, "Van Ness Cottages") ~ 1,
        invest_begin_07 == 1                             ~ 1,
        TRUE                                             ~ 0
      ),
    invest_begin_13 = 
      case_when(
        ## Mid City/Expo LRT
        str_detect(investment_name, "Exposition Line") ~ 1,
        invest_begin_10 == 1                           ~ 1,
        TRUE                                           ~ 0
      ),
    invest_begin_16 = 
       case_when(
        ## San Leandro Downtown-BART Pedestrian Interface 
        str_detect(investment_name, "San_Leandro")       ~ 1,
        ## Cultural Arts District Park
        str_detect(investment_name, "Cultural Arts")     ~ 1,
        ## South Sacramento Corridor Light Rail Extension Phase 2
        str_detect(investment_name, "Phase 2")           ~ 1,    
        ## Metro Gold Line Foothill Extension (Phase 2A)
        str_detect(investment_name, "Gold_Line")         ~ 1,
        ## Taylor Yard Village
        str_detect(investment_name, "Taylor Yard")       ~ 1,
        str_detect(investment_name, "TYTV")              ~ 1,
        ## El Monte Transit Village
        str_detect(investment_name, "El Monte Transit" ) ~ 1,
        invest_begin_13 == 1                             ~ 1,
        TRUE                                             ~ 0
      ),
    invest_begin_18 =
      case_when(
        ## Fulton Mall Reconstruction Project
        str_detect(investment_name, "fulton mall")       ~ 1,
        ## Metro Willowbrook/Rosa Parks Station Improvements
        str_detect(investment_name, "Willowbrook_Rosa" ) ~ 1,
        ## Albion Riverside Park
        str_detect(investment_name, "albion riverside" ) ~ 1,
        ## Fresno BRT Improvements
        str_detect(investment_name, "Fresno BRT")        ~ 1,
        invest_begin_16 == 1                             ~ 1,
        TRUE                                             ~ 0
    )
  ) %>%
  # create # of investments in tract
  mutate(investment_no = glue("investment_{1:7}")) %>%
  # pivot to create unique rows (by tract)
  pivot_wider(
    names_from = investment_no,
    values_from = investment_name
  ) %>%
  # filter out repeated tracts
  # (equivalent to NA value of investment 1)
  filter(!(is.na(investment_1) & investment == 1)) %>%
  # need to ungroup GEOID
  ungroup()
```

# Housing Affordability (NOAH)
## Full models (NOAH)
```{r create-noah-var-names, results="asis", warning=FALSE, message=FALSE}
# Create shortcuts for reg models based on year
vars_00 <-
  total_reg_df %>% 
  select(matches("_00")) %>% 
  select(!matches("noah")) %>%
  names() %>% 
  paste(collapse = " + ")

vars_09 <-
  total_reg_df %>% 
  select(matches("_09")) %>% 
  select(-matches("noah")) %>% 
  names() %>% 
  paste(collapse = " + ")
```

### NOAH 2000 - 2009
```{r create-full-reg-models-00-09, results="asis", warning=FALSE, message=FALSE}
# NOAH 2000-2009
## create string of dependent variables
ivs_00 <- paste("investment + la_flag + sf_flag +",  vars_00)

## linear regression on NOAH percent change
perc_noah_00_reg <- 
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg <- 
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df
  )

## linear regression on NOAH unit change
unit_noah_00_reg <- 
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df
  )
```

```{r print-full-reg-models-00-09, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg,
  perc_pnt_noah_00_reg, 
  unit_noah_00_reg,
  type = "text",
  title = "NOAH Change 2000 - 2009 in Total Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016
```{r create-full-reg-models-09-16, results="asis", warning=FALSE, message=FALSE}
# NOAH 2009-2016
## create string of dependent variables
ivs_09 <- paste("investment + la_flag + sf_flag +",  vars_09)

## linear regression on NOAH percent change
perc_noah_09_reg <-
  lm(
    formula(paste("perc_noah_tot_change_09_16 ~", ivs_09)),
    total_reg_df
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg <-
  lm(
    formula(paste("perc_pnt_noah_change_09_16 ~", ivs_09)),
    total_reg_df
  )

## linear regression on NOAH unit change
unit_noah_09_reg <-
  lm(
    formula(paste("noah_tot_change_09_16 ~", ivs_09)),
    total_reg_df
  )
```

```{r print-full-reg-models-09-16, results="asis", warning=FALSE, message=FALSE}
# Reg table
stargazer::stargazer(
  perc_noah_09_reg,
  perc_pnt_noah_09_reg,
  unit_noah_09_reg,
  type = "html",
  title = "NOAH Change 2009 - 2016 in Total Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

## Models by investment (NOAH)
### NOAH 2000 - 2009
```{r create-invest-model-00-09, results="asis", warning=FALSE, message=FALSE}
# NOAH 2000-2009 by investment
## create string of dependent variables
ivs_00 <-
  paste(
    "la_flag + sf_flag + greening + transit + urban_infill + active_transportation +",
    vars_00
  )

## linear regression on NOAH percent change
perc_noah_00_reg <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df
  )

## linear regression on NOAH unit change
unit_noah_00_reg <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df
  )
```

```{r print-invest-model-00-09, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg,
  perc_pnt_noah_00_reg,
  unit_noah_00_reg,
  type = "html",
  title = "NOAH Change 2000 - 2009 in Total Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016
```{r create-invest-model-09-16, results="asis", warning=FALSE, message=FALSE}
# NOAH 2009-2016
## create string of dependent variables
ivs_09 <-
  paste(
    "la_flag + sf_flag + greening + transit + urban_infill + active_transportation +",
    vars_09
  )

## linear regression on NOAH percent change
perc_noah_09_reg <-
  lm(
    formula(paste("perc_noah_tot_change_09_16 ~", ivs_09)),
    total_reg_df
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg <-
  lm(
    formula(paste("perc_pnt_noah_change_09_16 ~", ivs_09)),
    total_reg_df
  )

## linear regression on NOAH unit change
unit_noah_09_reg <-
  lm(
    formula(paste("noah_tot_change_09_16 ~", ivs_09)),
    total_reg_df
  )
```

```{r print-invest-model-09-16, results="asis", warning=FALSE, message=FALSE}
# Reg table
stargazer::stargazer(
  perc_noah_09_reg,
  perc_pnt_noah_09_reg,
  unit_noah_09_reg,
  type = "html",
  title = "NOAH Change 2009 - 2016 in Total Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

## Models by metropolitan area (NOAH)
```{r create-metro-model-00-09, results="asis", warning=FALSE, message=FALSE}
# NOAH 2000-2009 by metro area
## create string of dependent variables
ivs_00 <- paste("investment +", vars_00)

# LA Models
## linear regression on NOAH percent change
perc_noah_00_reg_la <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_la <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_la <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

# Fresno Models
## linear regression on NOAH percent change
perc_noah_00_reg_fresno <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_fresno <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_fresno <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

# SF Bay Models
## linear regression on NOAH percent change
perc_noah_00_reg_sf <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_sf <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_sf <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )
```

### NOAH 2000 - 2009 (LA)
```{r print-metro-model-00-09-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_la,
  perc_pnt_noah_00_reg_la,
  unit_noah_00_reg_la,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the LA Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2000 - 2009 (Fresno)
```{r print-metro-model-00-09-fresno}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_fresno,
  perc_pnt_noah_00_reg_fresno,
  unit_noah_00_reg_fresno,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the Fresno Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2000 - 2009 (SF Bay Area)
```{r print-metro-model-00-09-sf}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_sf,
  perc_pnt_noah_00_reg_sf,
  unit_noah_00_reg_sf,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the SF Bay Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

```{r create-metro-model-09-16, results="asis", warning=FALSE, message=FALSE}
# NOAH 2009-2016
## create string of dependent variables
ivs_09 <-
  paste("investment +", vars_09)

# LA Models
## linear regression on NOAH percent change
perc_noah_09_reg_la <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_la <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_la <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

# Fresno Models
## linear regression on NOAH percent change
perc_noah_09_reg_fresno <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_fresno <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_fresno <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

# SF Bay Models
## linear regression on NOAH percent change
perc_noah_09_reg_sf <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_sf <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_sf <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )
```

### NOAH 2009 - 2016 (LA)
```{r print-metro-model-09-16-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_la,
  perc_pnt_noah_09_reg_la,
  unit_noah_09_reg_la,
  type = "html",
  title = "NOAH Change 2009 - 2016 in the LA Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016 (Fresno)
```{r print-metro-model-09-16-fresno}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_fresno,
  perc_pnt_noah_09_reg_fresno,
  unit_noah_09_reg_fresno,
  type = "html",
  title = "NOAH Change 2009 - 2016 in the Fresno Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016 (SF Bay Area)
```{r print-metro-model-09-16-sf}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_sf,
  perc_pnt_noah_09_reg_sf,
  unit_noah_09_reg_sf,
  type = "html",
  title = "NOAH Change 2000 - 2016 in the SF Bay Area",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

## Models by investment and metropolitan area (NOAH)
```{r create-invest-metro-model-00-09, results="asis", warning=FALSE, message=FALSE}
# NOAH 2000-2009 by metro area
## create string of dependent variables
ivs_00 <-
  paste(
    "greening + transit + urban_infill + active_transportation +",
    vars_00
  )

# LA Models
## linear regression on NOAH percent change
perc_noah_00_reg_la <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_la <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_la <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 1)
  )

# Fresno Models
## linear regression on NOAH percent change
perc_noah_00_reg_fresno <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_fresno <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_fresno <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

# SF Bay Models
## linear regression on NOAH percent change
perc_noah_00_reg_sf <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_00_reg_sf <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_00_reg_sf <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_00)),
    total_reg_df %>% filter(sf_flag == 1)
  )
```

### NOAH 2000 - 2009 (LA)
```{r print-invest-metro-model-00-09-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_la,
  perc_pnt_noah_00_reg_la,
  unit_noah_00_reg_la,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the LA Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2000 - 2009 (Fresno)
```{r print-invest-metro-model-00-09-fresno}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_fresno,
  perc_pnt_noah_00_reg_fresno,
  unit_noah_00_reg_fresno,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the Fresno Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2000 - 2009 (SF Bay Area)
```{r print-invest-metro-model-00-09-sf}
# Print reg table
stargazer::stargazer(
  perc_noah_00_reg_sf,
  perc_pnt_noah_00_reg_sf,
  unit_noah_00_reg_sf,
  type = "html",
  title = "NOAH Change 2000 - 2009 in the SF Bay Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

```{r create-invest-metro-model-09-16, results="asis", warning=FALSE, message=FALSE}
# NOAH 2009-2016
## create string of dependent variables
ivs_09 <-
  paste(
    "greening + transit + urban_infill + active_transportation +",
    vars_09
  )

# LA Models
## linear regression on NOAH percent change
perc_noah_09_reg_la <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_la <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_la <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 1)
  )

# Fresno Models
## linear regression on NOAH percent change
perc_noah_09_reg_fresno <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_fresno <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_fresno <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(la_flag == 0 & sf_flag == 0)
  )

# SF Bay Models
## linear regression on NOAH percent change
perc_noah_09_reg_sf <-
  lm(
    formula(paste("perc_noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH percentage point change
perc_pnt_noah_09_reg_sf <-
  lm(
    formula(paste("perc_pnt_noah_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )

## linear regression on NOAH unit change
unit_noah_09_reg_sf <-
  lm(
    formula(paste("noah_tot_change_00_09 ~", ivs_09)),
    total_reg_df %>% filter(sf_flag == 1)
  )
```

### NOAH 2009 - 2016 (LA)
```{r print-invest-metro-model-09-16-la}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_la,
  perc_pnt_noah_09_reg_la,
  unit_noah_09_reg_la,
  type = "html",
  title = "NOAH Change 2009 - 2016 in the LA Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016 (Fresno)
```{r print-invest-metro-model-09-16-fresno}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_fresno,
  perc_pnt_noah_09_reg_fresno,
  unit_noah_09_reg_fresno,
  type = "html",
  title = "NOAH Change 2009 - 2016 in the Fresno Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

### NOAH 2009 - 2016 (SF Bay Area)
```{r print-invest-metro-model-09-16-sf}
# Print reg table
stargazer::stargazer(
  perc_noah_09_reg_sf,
  perc_pnt_noah_09_reg_sf,
  unit_noah_09_reg_sf,
  type = "html",
  title = "NOAH Change 2009 - 2016 in the SF Bay Area by Investment Type",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("PERCENT", "PERCENTAGE POINT", "UNIT")
)
```

# Displacement OLS (Outmigration)
## Full models (OLS - Outmigration)
```{r create-outmig-var-names, results="asis", warning=FALSE, message=FALSE}
# Create shortcuts for reg models based on year
vars_07 <-
  total_reg_df %>%
  select(matches("_09")) %>%
  select(-matches("noah")) %>%
  names() %>%
  paste(collapse = " + ")

vars_10 <-
  total_reg_df %>%
  select(matches("_10")) %>%
  select(-matches("noah")) %>%
  names() %>%
  paste(collapse = " + ")

vars_13 <-
  total_reg_df %>%
  select(matches("_13")) %>%
  select(-matches("noah")) %>%
  names() %>%
  paste(collapse = " + ")

vars_16 <-
  total_reg_df %>%
  select(matches("_16")) %>%
  select(-matches("noah")) %>%
  names() %>%
  paste(collapse = " + ")

vars_18 <-
  total_reg_df %>%
  select(matches("_18")) %>%
  select(-matches("noah")) %>%
  names() %>%
  paste(collapse = " + ")
```

```{r create-outmig-model-helper-func}
# helper function for outmigration regs
outmigration_reg_full_ols <- function(df, vars_year, year, outmig_type, area_ivs = c(), type_ivs = c()) {
  year <- enquo(year)
  outmig_type <- enquo(outmig_type)

  ## create string of independent variables
  ivs <- paste("investment +", vars_year)

  ## Attach study area IVs if needed
  if (length(area_ivs) != 0){
    ivs <- paste(area_ivs, ivs, sep = " + ")
  }

  ## Attach investment type IVs if needed
  if (length(type_ivs) != 0){
    ivs <- paste(type_ivs, ivs, sep = " + ")
  }

  ## linear regression on outmigration type
  outmig_reg <-
    lm(
      formula(
        paste0(
          "outmigration_",
          as_label(outmig_type),
          "_",
          as_label(year),
          " ~ ",
          ivs
        )
      ),
      df
    )
  return(outmig_reg)
}
```

### Outmigration 2007
```{r create-full-model-07, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_07, 2007, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_07, 2007, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_07, 2007, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_07, 2007, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-model-07, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_07_reg,
  outmig_li_07_reg,
  outmig_r_07_reg,
  outmig_li_r_07_reg,
  type = "html",
  title = "2007 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010
```{r create-full-model-10, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_10, 2010, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_10, 2010, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_10, 2010, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_10, 2010, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-model-10, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_10_reg,
  outmig_li_10_reg,
  outmig_r_10_reg,
  outmig_li_r_10_reg,
  type = "html",
  title = "2010 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013
```{r create-full-model-13, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_13, 2013, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_13, 2013, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_13, 2013, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_13, 2013, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-model-13, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_13_reg,
  outmig_li_13_reg,
  outmig_r_13_reg,
  outmig_li_r_13_reg,
  type = "html",
  title = "2013 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016
```{r create-full-model-16, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_16, 2016, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_16, 2016, LI, area_ivs = "la_flag + sf_flag",
  )

## linear regression on outmigration renters
outmig_r_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_16, 2016, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_16, 2016, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-model-16, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_16_reg,
  outmig_li_16_reg,
  outmig_r_16_reg,
  outmig_li_r_16_reg,
  type = "html",
  title = "2016 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018
```{r create-full-model-18, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_18, 2018, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_18, 2018, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_18, 2018, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df, vars_18, 2018, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-model-18, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_18_reg,
  outmig_li_18_reg,
  outmig_r_18_reg,
  outmig_li_r_18_reg,
  type = "html",
  title = "2018 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by investment (OLS - Outmigration)
### Outmigration 2007
```{r create-invest-model-07, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_07,
    2007,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_07,
    2007,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_07,
    2007,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_07,
    2007,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-model-07, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_07_reg,
  outmig_li_07_reg,
  outmig_r_07_reg,
  outmig_li_r_07_reg,
  type = "html",
  title = "2007 Outmigration Rate in Total Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010
```{r create-invest-model-10, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_10,
    2010,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_10,
    2010,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_10,
    2010,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_10,
    2010,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-model-10, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_10_reg,
  outmig_li_10_reg,
  outmig_r_10_reg,
  outmig_li_r_10_reg,
  type = "html",
  title = "2010 Outmigration Rate in Total Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013
```{r create-invest-model-13, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_13,
    2013,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_13,
    2013,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_13,
    2013,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_13,
    2013,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-model-13, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_13_reg,
  outmig_li_13_reg,
  outmig_r_13_reg,
  outmig_li_r_13_reg,
  type = "html",
  title = "2013 Outmigration Rate in Total Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016
```{r create-invest-model-16, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_16,
    2016,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_16,
    2016,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_16,
    2016,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_16,
    2016,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-model-16, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_16_reg,
  outmig_li_16_reg,
  outmig_r_16_reg,
  outmig_li_r_16_reg,
  type = "html",
  title = "2016 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018
```{r create-invest-model-18, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_18,
    2018,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_18,
    2018,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_18,
    2018,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg <-
  outmigration_reg_full_ols(
    total_reg_df,
    vars_18,
    2018,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-model-18, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_18_reg,
  outmig_li_18_reg,
  outmig_r_18_reg,
  outmig_li_r_18_reg,
  type = "html",
  title = "2018 Outmigration Rate in Total Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by metropolitan area (OLS - Outmigration)
```{r create-metro-model-07, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, LI_renters
  )

# SF Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, LI_renters
  )


# Fresno Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_07,
   2007,
   LI_renters
  )
```

### Outmigration 2007 (LA)
```{r print-metro-model-07-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_07_reg_la,
  outmig_li_07_reg_la,
  outmig_r_07_reg_la,
  outmig_li_r_07_reg_la,
  type = "html",
  title = "2007 Outmigration Rate in the LA Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (SF)
```{r print-metro-model-07-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_07_reg_sf,
  outmig_li_07_reg_sf,
  outmig_r_07_reg_sf,
  outmig_li_r_07_reg_sf,
  type = "html",
  title = "2007 Outmigration Rate in the SF Bay Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (Fresno)
```{r print-metro-model-07-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_07_reg_fresno,
  outmig_li_07_reg_fresno,
  outmig_r_07_reg_fresno,
  outmig_li_r_07_reg_fresno,
  type = "html",
  title = "2007 Outmigration Rate in the Fresno Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-model-10, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, LI_renters
  )

# SF Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, LI_renters
  )

# Fresno Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_10,
   2010,
   LI_renters
  )
```

### Outmigration 2010 (LA)
```{r print-metro-model-10-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_10_reg_la,
  outmig_li_10_reg_la,
  outmig_r_10_reg_la,
  outmig_li_r_10_reg_la,
  type = "html",
  title = "2010 Outmigration Rate in the LA Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (SF Bay Area)
```{r print-metro-model-10-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_10_reg_sf,
  outmig_li_10_reg_sf,
  outmig_r_10_reg_sf,
  outmig_li_r_10_reg_sf,
  type = "html",
  title = "2010 Outmigration Rate in the SF Bay Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (Fresno)
```{r print-metro-model-10-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_10_reg_fresno,
  outmig_li_10_reg_fresno,
  outmig_r_10_reg_fresno,
  outmig_li_r_10_reg_fresno,
  type = "html",
  title = "2010 Outmigration Rate in the Fresno Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-model-13, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, LI_renters
  )

# SF Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, LI_renters
  )

# Fresno Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_13,
   2013,
   LI_renters
  )
```

### Outmigration 2013 (LA)
```{r print-metro-model-13-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_13_reg_la,
  outmig_li_13_reg_la,
  outmig_r_13_reg_la,
  outmig_li_r_13_reg_la,
  type = "html",
  title = "2013 Outmigration Rate in the LA Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (SF Bay Area)
```{r print-metro-model-13-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_13_reg_sf,
  outmig_li_13_reg_sf,
  outmig_r_13_reg_sf,
  outmig_li_r_13_reg_sf,
  type = "html",
  title = "2013 Outmigration Rate in the SF Bay Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (Fresno)
```{r print-metro-model-13-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_13_reg_fresno,
  outmig_li_13_reg_fresno,
  outmig_r_13_reg_fresno,
  outmig_li_r_13_reg_fresno,
  type = "html",
  title = "2013 Outmigration Rate in the Fresno Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-model-16, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, LI_renters
  )

# SF Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, LI_renters
  )

# Fresno Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_16,
   2016,
   LI_renters
  )
```

### Outmigration 2016 (LA)
```{r print-metro-model-16-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_16_reg_la,
  outmig_li_16_reg_la,
  outmig_r_16_reg_la,
  outmig_li_r_16_reg_la,
  type = "html",
  title = "2016 Outmigration Rate in the LA Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (SF Bay Area)
```{r print-metro-model-16-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_16_reg_sf,
  outmig_li_16_reg_sf,
  outmig_r_16_reg_sf,
  outmig_li_r_16_reg_sf,
  type = "html",
  title = "2016 Outmigration Rate in the SF Bay Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (Fresno)
```{r print-metro-model-16-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_16_reg_fresno,
  outmig_li_16_reg_fresno,
  outmig_r_16_reg_fresno,
  outmig_li_r_16_reg_fresno,
  type = "html",
  title = "2016 Outmigration Rate in the Fresno Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-model-18, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, LI_renters
  )

# SF Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, LI_renters
  )

# Fresno Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_18,
   2018,
   LI_renters
  )
```

### Outmigration 2018 (LA)
```{r print-metro-model-18-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_18_reg_la,
  outmig_li_18_reg_la,
  outmig_r_18_reg_la,
  outmig_li_r_18_reg_la,
  type = "html",
  title = "2018 Outmigration Rate in the LA Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (SF Bay Area)
```{r print-metro-model-18-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_18_reg_sf,
  outmig_li_18_reg_sf,
  outmig_r_18_reg_sf,
  outmig_li_r_18_reg_sf,
  type = "html",
  title = "2018 Outmigration Rate in the SF Bay Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (Fresno)
```{r print-metro-model-18-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_18_reg_fresno,
  outmig_li_18_reg_fresno,
  outmig_r_18_reg_fresno,
  outmig_li_r_18_reg_fresno,
  type = "html",
  title = "2018 Outmigration Rate in the Fresno Area (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by investment and metropolitan area (OLS - Outmigration)
```{r create-invest-metro-model-07, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_07,
   2007,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2007 (LA)
```{r print-invest-metro-model-07-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_07_reg_la,
  outmig_li_07_reg_la,
  outmig_r_07_reg_la,
  outmig_li_r_07_reg_la,
  type = "html",
  title = "2007 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (SF Bay Area)
```{r print-invest-metro-model-07-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_07_reg_sf,
  outmig_li_07_reg_sf,
  outmig_r_07_reg_sf,
  outmig_li_r_07_reg_sf,
  type = "html",
  title = "2007 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (Fresno)
```{r print-invest-metro-model-07-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_07_reg_fresno,
  outmig_li_07_reg_fresno,
  outmig_r_07_reg_fresno,
  outmig_li_r_07_reg_fresno,
  type = "html",
  title = "2007 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-model-10, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_10,
   2010,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2010 (LA)
```{r print-invest-metro-model-10-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_10_reg_la,
  outmig_li_10_reg_la,
  outmig_r_10_reg_la,
  outmig_li_r_10_reg_la,
  type = "html",
  title = "2010 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (SF)
```{r print-invest-metro-model-10-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_10_reg_sf,
  outmig_li_10_reg_sf,
  outmig_r_10_reg_sf,
  outmig_li_r_10_reg_sf,
  type = "html",
  title = "2010 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (Fresno)
```{r print-invest-metro-model-10-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_10_reg_fresno,
  outmig_li_10_reg_fresno,
  outmig_r_10_reg_fresno,
  outmig_li_r_10_reg_fresno,
  type = "html",
  title = "2010 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-model-13, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2013 (ACS 2009)
## linear regression on outmigration all
outmig_all_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2013 (ACS 2009)
## linear regression on outmigration all
outmig_all_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_13,
   2013,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2013 (LA)
```{r print-invest-metro-model-13-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_13_reg_la,
  outmig_li_13_reg_la,
  outmig_r_13_reg_la,
  outmig_li_r_13_reg_la,
  type = "html",
  title = "2013 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (SF Bay Area)
```{r print-invest-metro-model-13-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_13_reg_sf,
  outmig_li_13_reg_sf,
  outmig_r_13_reg_sf,
  outmig_li_r_13_reg_sf,
  type = "html",
  title = "2013 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (Fresno)
```{r print-invest-metro-model-13-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_13_reg_fresno,
  outmig_li_13_reg_fresno,
  outmig_r_13_reg_fresno,
  outmig_li_r_13_reg_fresno,
  type = "html",
  title = "2013 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-model-16, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_16,
   2016,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2016 (LA)
```{r print-invest-metro-model-16-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_16_reg_la,
  outmig_li_16_reg_la,
  outmig_r_16_reg_la,
  outmig_li_r_16_reg_la,
  type = "html",
  title = "2016 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (SF Bay Area)
```{r print-invest-metro-model-16-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_16_reg_sf,
  outmig_li_16_reg_sf,
  outmig_r_16_reg_sf,
  outmig_li_r_16_reg_sf,
  type = "html",
  title = "2016 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (Fresno)
```{r print-invest-metro-model-16-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_16_reg_fresno,
  outmig_li_16_reg_fresno,
  outmig_r_16_reg_fresno,
  outmig_li_r_16_reg_fresno,
  type = "html",
  title = "2016 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-model-18, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_la <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_sf <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2018 (ACS 2009)
## linear regression on outmigration all
outmig_all_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_fresno <-
  outmigration_reg_full_ols(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_fresno <-
  outmigration_reg_full_ols(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_18,
   2018,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2018 (LA)
```{r print-invest-metro-model-18-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_18_reg_la,
  outmig_li_18_reg_la,
  outmig_r_18_reg_la,
  outmig_li_r_18_reg_la,
  type = "html",
  title = "2018 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (SF Bay Area)
```{r print-invest-metro-model-18-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_18_reg_sf,
  outmig_li_18_reg_sf,
  outmig_r_18_reg_sf,
  outmig_li_r_18_reg_sf,
  type = "html",
  title = "2018 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (Fresno)
```{r print-invest-metro-model-18-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_18_reg_fresno,
  outmig_li_18_reg_fresno,
  outmig_r_18_reg_fresno,
  outmig_li_r_18_reg_fresno,
  type = "html",
  title = "2018 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

# Displacement Fixed Effects (Outmigration)
## Full models (fixed effects - Outmigration)
```{r create-outmig-fixed-helper-func}
# helper function for outmigration regs
outmigration_reg_full_fixed <- function(df, vars_year, year, outmig_type, area_ivs = c(), type_ivs = c()) {
  year <- enquo(year)
  outmig_type <- enquo(outmig_type)

  ## create string of independent variables
  ivs <- 
    paste(
      "invest_begin_07 + invest_begin_10 + invest_begin_13 + invest_begin_16 + invest_begin_18 +",
      vars_year
    )

  ## Attach study area IVs if needed
  if (length(area_ivs) != 0){
    ivs <- paste(area_ivs, ivs, sep = " + ")
  }

  ## Attach investment type IVs if needed
  if (length(type_ivs) != 0){
    ivs <- paste(type_ivs, ivs, sep = " + ")
  }

  ## linear regression on outmigration type
  outmig_reg <-
    lm(
      formula(
        paste0(
          "outmigration_",
          as_label(outmig_type),
          "_",
          as_label(year),
          " ~ ",
          ivs
        )
      ),
      df
    )
  return(outmig_reg)
}
```

### Outmigration 2007
```{r create-full-fixed-07, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_07, 2007, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_07, 2007, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_07, 2007, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_07, 2007, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-fixed-07, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_07_reg,
  outmig_li_07_reg,
  outmig_r_07_reg,
  outmig_li_r_07_reg,
  type = "html",
  title = "2007 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010
```{r create-full-fixed-10, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_10, 2010, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_10, 2010, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_10, 2010, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_10, 2010, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-fixed-10, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_10_reg,
  outmig_li_10_reg,
  outmig_r_10_reg,
  outmig_li_r_10_reg,
  type = "html",
  title = "2010 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013
```{r create-full-fixed-13, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_13, 2013, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_13, 2013, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_13, 2013, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_13, 2013, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-fixed-13, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_13_reg,
  outmig_li_13_reg,
  outmig_r_13_reg,
  outmig_li_r_13_reg,
  type = "html",
  title = "2013 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016
```{r create-full-fixed-16, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_16, 2016, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_16, 2016, LI, area_ivs = "la_flag + sf_flag",
  )

## linear regression on outmigration renters
outmig_r_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_16, 2016, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_16, 2016, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-fixed-16, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_16_reg,
  outmig_li_16_reg,
  outmig_r_16_reg,
  outmig_li_r_16_reg,
  type = "html",
  title = "2016 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018
```{r create-full-fixed-18, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_18, 2018, all, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI
outmig_li_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_18, 2018, LI, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration renters
outmig_r_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_18, 2018, renters, area_ivs = "la_flag + sf_flag"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df, vars_18, 2018, LI_renters, area_ivs = "la_flag + sf_flag"
  )
```

```{r print-full-fixed-18, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_18_reg,
  outmig_li_18_reg,
  outmig_r_18_reg,
  outmig_li_r_18_reg,
  type = "html",
  title = "2018 Outmigration Rate in Total Area (Full Fixed)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by investment (fixed effects - Outmigration)
### Outmigration 2007
```{r create-invest-fixed-07, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_07,
    2007,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_07,
    2007,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_07,
    2007,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_07,
    2007,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-fixed-07, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_07_reg,
  outmig_li_07_reg,
  outmig_r_07_reg,
  outmig_li_r_07_reg,
  type = "html",
  title = 
    "2007 Outmigration Rate in Total Area by Investment Type (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010
```{r create-invest-fixed-10, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_10,
    2010,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_10,
    2010,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_10,
    2010,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_10,
    2010,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-fixed-10, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_10_reg,
  outmig_li_10_reg,
  outmig_r_10_reg,
  outmig_li_r_10_reg,
  type = "html",
  title = 
    "2010 Outmigration Rate in Total Area by Investment Type (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013
```{r create-invest-fixed-13, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_13,
    2013,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_13,
    2013,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_13,
    2013,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_13,
    2013,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-fixed-13, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_13_reg,
  outmig_li_13_reg,
  outmig_r_13_reg,
  outmig_li_r_13_reg,
  type = "html",
  title = 
    "2013 Outmigration Rate in Total Area by Investment Type (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016
```{r create-invest-fixed-16, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_16,
    2016,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_16,
    2016,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_16,
    2016,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_16,
    2016,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-fixed-16, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_16_reg,
  outmig_li_16_reg,
  outmig_r_16_reg,
  outmig_li_r_16_reg,
  type = "html",
  title = "2016 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018
```{r create-invest-fixed-18, results="asis", warning=FALSE, message=FALSE}
# Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_18,
    2018,
    all,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_18,
    2018,
    LI,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_18,
    2018,
    renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg <-
  outmigration_reg_full_fixed(
    total_reg_df,
    vars_18,
    2018,
    LI_renters,
    area_ivs = "la_flag + sf_flag",
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

```{r print-invest-fixed-18, results="asis", warning=FALSE, message=FALSE}
# Print reg table
stargazer::stargazer(
  outmig_all_18_reg,
  outmig_li_18_reg,
  outmig_r_18_reg,
  outmig_li_r_18_reg,
  type = "html",
  title = "2018 Outmigration Rate in Total Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by metropolitan area (fixed effects - Outmigration)
```{r create-metro-fixed-07, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_07, 2007, LI_renters
  )

# SF Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_07, 2007, LI_renters
  )


# Fresno Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, all
  )

## linear regression on outmigration LI
outmig_li_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, LI
  )

## linear regression on outmigration renters
outmig_r_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_07, 2007, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_07,
   2007,
   LI_renters
  )
```

### Outmigration 2007 (LA)
```{r print-metro-fixed-07-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_07_reg_la,
  outmig_li_07_reg_la,
  outmig_r_07_reg_la,
  outmig_li_r_07_reg_la,
  type = "html",
  title = "2007 Outmigration Rate in the LA Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (SF)
```{r print-metro-fixed-07-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_07_reg_sf,
  outmig_li_07_reg_sf,
  outmig_r_07_reg_sf,
  outmig_li_r_07_reg_sf,
  type = "html",
  title = "2007 Outmigration Rate in the SF Bay Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (Fresno)
```{r print-metro-fixed-07-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_07_reg_fresno,
  outmig_li_07_reg_fresno,
  outmig_r_07_reg_fresno,
  outmig_li_r_07_reg_fresno,
  type = "html",
  title = "2007 Outmigration Rate in the Fresno Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-fixed-10, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_10, 2010, LI_renters
  )

# SF Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_10, 2010, LI_renters
  )

# Fresno Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, all
  )

## linear regression on outmigration LI
outmig_li_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, LI
  )

## linear regression on outmigration renters
outmig_r_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_10, 2010, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_10,
   2010,
   LI_renters
  )
```

### Outmigration 2010 (LA)
```{r print-metro-fixed-10-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_10_reg_la,
  outmig_li_10_reg_la,
  outmig_r_10_reg_la,
  outmig_li_r_10_reg_la,
  type = "html",
  title = "2010 Outmigration Rate in the LA Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (SF Bay Area)
```{r print-metro-fixed-10-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_10_reg_sf,
  outmig_li_10_reg_sf,
  outmig_r_10_reg_sf,
  outmig_li_r_10_reg_sf,
  type = "html",
  title = "2010 Outmigration Rate in the SF Bay Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (Fresno)
```{r print-metro-fixed-10-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_10_reg_fresno,
  outmig_li_10_reg_fresno,
  outmig_r_10_reg_fresno,
  outmig_li_r_10_reg_fresno,
  type = "html",
  title = "2010 Outmigration Rate in the Fresno Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-fixed-13, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_13, 2013, LI_renters
  )

# SF Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_13, 2013, LI_renters
  )

# Fresno Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, all
  )

## linear regression on outmigration LI
outmig_li_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, LI
  )

## linear regression on outmigration renters
outmig_r_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_13, 2013, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_13,
   2013,
   LI_renters
  )
```

### Outmigration 2013 (LA)
```{r print-metro-fixed-13-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_13_reg_la,
  outmig_li_13_reg_la,
  outmig_r_13_reg_la,
  outmig_li_r_13_reg_la,
  type = "html",
  title = "2013 Outmigration Rate in the LA Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (SF Bay Area)
```{r print-metro-fixed-13-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_13_reg_sf,
  outmig_li_13_reg_sf,
  outmig_r_13_reg_sf,
  outmig_li_r_13_reg_sf,
  type = "html",
  title = "2013 Outmigration Rate in the SF Bay Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (Fresno)
```{r print-metro-fixed-13-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_13_reg_fresno,
  outmig_li_13_reg_fresno,
  outmig_r_13_reg_fresno,
  outmig_li_r_13_reg_fresno,
  type = "html",
  title = "2013 Outmigration Rate in the Fresno Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-fixed-16, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_16, 2016, LI_renters
  )

# SF Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_16, 2016, LI_renters
  )

# Fresno Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, all
  )

## linear regression on outmigration LI
outmig_li_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, LI
  )

## linear regression on outmigration renters
outmig_r_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_16, 2016, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_16,
   2016,
   LI_renters
  )
```

### Outmigration 2016 (LA)
```{r print-metro-fixed-16-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_16_reg_la,
  outmig_li_16_reg_la,
  outmig_r_16_reg_la,
  outmig_li_r_16_reg_la,
  type = "html",
  title = "2016 Outmigration Rate in the LA Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (SF Bay Area)
```{r print-metro-fixed-16-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_16_reg_sf,
  outmig_li_16_reg_sf,
  outmig_r_16_reg_sf,
  outmig_li_r_16_reg_sf,
  type = "html",
  title = "2016 Outmigration Rate in the SF Bay Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (Fresno)
```{r print-metro-fixed-16-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_16_reg_fresno,
  outmig_li_16_reg_fresno,
  outmig_r_16_reg_fresno,
  outmig_li_r_16_reg_fresno,
  type = "html",
  title = "2016 Outmigration Rate in the Fresno Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-metro-fixed-18, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1), vars_18, 2018, LI_renters
  )

# SF Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1), vars_18, 2018, LI_renters
  )

# Fresno Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, all
  )

## linear regression on outmigration LI
outmig_li_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, LI
  )

## linear regression on outmigration renters
outmig_r_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0), vars_18, 2018, renters
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_18,
   2018,
   LI_renters
  )
```

### Outmigration 2018 (LA)
```{r print-metro-fixed-18-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_18_reg_la,
  outmig_li_18_reg_la,
  outmig_r_18_reg_la,
  outmig_li_r_18_reg_la,
  type = "html",
  title = "2018 Outmigration Rate in the LA Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (SF Bay Area)
```{r print-metro-fixed-18-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_18_reg_sf,
  outmig_li_18_reg_sf,
  outmig_r_18_reg_sf,
  outmig_li_r_18_reg_sf,
  type = "html",
  title = "2018 Outmigration Rate in the SF Bay Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (Fresno)
```{r print-metro-fixed-18-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_18_reg_fresno,
  outmig_li_18_reg_fresno,
  outmig_r_18_reg_fresno,
  outmig_li_r_18_reg_fresno,
  type = "html",
  title = "2018 Outmigration Rate in the Fresno Area (Fixed Effects)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

## Models by investment and metropolitan area (fixed effects - Outmigration)
```{r create-invest-metro-fixed-07, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_07,
    2007,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_07,
    2007,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2007 (ACS 2009)
## linear regression on outmigration all
outmig_all_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_07_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_07,
    2007,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_07_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_07,
   2007,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2007 (LA)
```{r print-invest-metro-fixed-07-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_07_reg_la,
  outmig_li_07_reg_la,
  outmig_r_07_reg_la,
  outmig_li_r_07_reg_la,
  type = "html",
  title = "2007 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (SF Bay Area)
```{r print-invest-metro-fixed-07-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_07_reg_sf,
  outmig_li_07_reg_sf,
  outmig_r_07_reg_sf,
  outmig_li_r_07_reg_sf,
  type = "html",
  title = "2007 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2007 (Fresno)
```{r print-invest-metro-fixed-07-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_07_reg_fresno,
  outmig_li_07_reg_fresno,
  outmig_r_07_reg_fresno,
  outmig_li_r_07_reg_fresno,
  type = "html",
  title = "2007 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-fixed-10, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_10,
    2010,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_10,
    2010,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2010 (ACS 2010)
## linear regression on outmigration all
outmig_all_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_10_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_10,
    2010,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_10_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_10,
   2010,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2010 (LA)
```{r print-invest-metro-fixed-10-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_10_reg_la,
  outmig_li_10_reg_la,
  outmig_r_10_reg_la,
  outmig_li_r_10_reg_la,
  type = "html",
  title = "2010 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (SF)
```{r print-invest-metro-fixed-10-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_10_reg_sf,
  outmig_li_10_reg_sf,
  outmig_r_10_reg_sf,
  outmig_li_r_10_reg_sf,
  type = "html",
  title = "2010 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2010 (Fresno)
```{r print-invest-metro-fixed-10-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_10_reg_fresno,
  outmig_li_10_reg_fresno,
  outmig_r_10_reg_fresno,
  outmig_li_r_10_reg_fresno,
  type = "html",
  title = "2010 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-fixed-13, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2013 (ACS 2013)
## linear regression on outmigration all
outmig_all_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_13,
    2013,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2013 (ACS 2009)
## linear regression on outmigration all
outmig_all_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_13,
    2013,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2013 (ACS 2009)
## linear regression on outmigration all
outmig_all_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_13_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_13,
    2013,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_13_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_13,
   2013,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2013 (LA)
```{r print-invest-metro-fixed-13-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_13_reg_la,
  outmig_li_13_reg_la,
  outmig_r_13_reg_la,
  outmig_li_r_13_reg_la,
  type = "html",
  title = "2013 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (SF Bay Area)
```{r print-invest-metro-fixed-13-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_13_reg_sf,
  outmig_li_13_reg_sf,
  outmig_r_13_reg_sf,
  outmig_li_r_13_reg_sf,
  type = "html",
  title = "2013 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2013 (Fresno)
```{r print-invest-metro-fixed-13-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_13_reg_fresno,
  outmig_li_13_reg_fresno,
  outmig_r_13_reg_fresno,
  outmig_li_r_13_reg_fresno,
  type = "html",
  title = "2013 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-fixed-16, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_16,
    2016,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_16,
    2016,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2016 (ACS 2016)
## linear regression on outmigration all
outmig_all_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_16_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_16,
    2016,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_16_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_16,
   2016,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2016 (LA)
```{r print-invest-metro-fixed-16-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_16_reg_la,
  outmig_li_16_reg_la,
  outmig_r_16_reg_la,
  outmig_li_r_16_reg_la,
  type = "html",
  title = "2016 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (SF Bay Area)
```{r print-invest-metro-fixed-16-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_16_reg_sf,
  outmig_li_16_reg_sf,
  outmig_r_16_reg_sf,
  outmig_li_r_16_reg_sf,
  type = "html",
  title = "2016 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2016 (Fresno)
```{r print-invest-metro-fixed-16-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_16_reg_fresno,
  outmig_li_16_reg_fresno,
  outmig_r_16_reg_fresno,
  outmig_li_r_16_reg_fresno,
  type = "html",
  title = "2016 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

```{r create-invest-metro-fixed-18, results="asis", warning=FALSE, message=FALSE}
# LA Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_la <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(la_flag == 1),
    vars_18,
    2018,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

# SF Outmigration 2018 (ACS 2018)
## linear regression on outmigration all
outmig_all_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_sf <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 1),
    vars_18,
    2018,
    LI_renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )


# Fresno Outmigration 2018 (ACS 2009)
## linear regression on outmigration all
outmig_all_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    all,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI
outmig_li_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    LI,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration renters
outmig_r_18_reg_fresno <-
  outmigration_reg_full_fixed(
    total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
    vars_18,
    2018,
    renters,
    type_ivs = "greening + transit + urban_infill + active_transportation"
  )

## linear regression on outmigration LI renters
outmig_li_r_18_reg_fresno <-
  outmigration_reg_full_fixed(
   total_reg_df %>% filter(sf_flag == 0 & la_flag == 0),
   vars_18,
   2018,
   LI_renters,
   type_ivs = "greening + transit + urban_infill + active_transportation"
  )
```

### Outmigration 2018 (LA)
```{r print-invest-metro-fixed-18-la, results="asis", warning=FALSE, message=FALSE}
# Print reg table LA
stargazer::stargazer(
  outmig_all_18_reg_la,
  outmig_li_18_reg_la,
  outmig_r_18_reg_la,
  outmig_li_r_18_reg_la,
  type = "html",
  title = "2018 Outmigration Rate in the LA Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (SF Bay Area)
```{r print-invest-metro-fixed-18-sf, results="asis", warning=FALSE, message=FALSE}
# Print reg table SF
stargazer::stargazer(
  outmig_all_18_reg_sf,
  outmig_li_18_reg_sf,
  outmig_r_18_reg_sf,
  outmig_li_r_18_reg_sf,
  type = "html",
  title = "2018 Outmigration Rate in the SF Bay Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```

### Outmigration 2018 (Fresno)
```{r print-invest-metro-fixed-18-fresno, results="asis", warning=FALSE, message=FALSE}
# Print reg table Fresno
stargazer::stargazer(
  outmig_all_18_reg_fresno,
  outmig_li_18_reg_fresno,
  outmig_r_18_reg_fresno,
  outmig_li_r_18_reg_fresno,
  type = "html",
  title = "2018 Outmigration Rate in the Fresno Area by Investment Type (OLS)",
  font.size = "small",
  column.sep.width = "1pt",
  dep.var.labels.include = FALSE,
  column.labels = c("ALL", "LOW INCOME", "RENTER", "LOW INCOME RENTER")
)
```
